cardinalR: Generating interesting high-dimensional data structures

### 2025-05-01 paper-cardinalR.Rmd
Added all parameters for swissroll
Added initial trigonometric projections

```{r data-swissroll, echo=TRUE}
swissroll <- gen_swissroll(n = 1000, p = 4)
```

@@

>>>>

```{r data-swissroll, echo=TRUE}
swissroll <- gen_swissroll(n = 1000, p = 4, w = c(-1, 1))
```

@@

```{r data-crescent, echo=TRUE}
crescent <- gen_crescent(n = 1000, p = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(crescent)
```

```{r crescent-proj1}
scaled_data <- scale_data_manual(crescent)

crescent_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r crescent-proj2}

crescent_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r crescent-proj3}

crescent_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-crescent-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `crescent` data."}
#| fig-width: 15
#| fig-height: 5

crescent_proj1 + crescent_proj2 + crescent_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-curvycylinder, echo=TRUE}
curvycylinder <- gen_curvycylinder(n = 1000, p = 4, h = 10)
```

```{r, eval=FALSE}
langevitour::langevitour(curvycylinder)
```

```{r curvycylinder-proj1}
scaled_data <- scale_data_manual(curvycylinder)

curvycylinder_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r curvycylinder-proj2}

curvycylinder_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r curvycylinder-proj3}

curvycylinder_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-curvycylinder-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `curvycylinder` data."}
#| fig-width: 15
#| fig-height: 5

curvycylinder_proj1 + curvycylinder_proj2 + curvycylinder_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-sphericalspiral, echo=TRUE}
sphericalspiral <- gen_sphericalspiral(n = 1000, p = 4, spins = 1)
```

```{r, eval=FALSE}
langevitour::langevitour(sphericalspiral)
```

```{r sphericalspiral-proj1}
scaled_data <- scale_data_manual(sphericalspiral)

sphericalspiral_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r sphericalspiral-proj2}

sphericalspiral_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r sphericalspiral-proj3}

sphericalspiral_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-sphericalspiral-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `sphericalspiral` data."}
#| fig-width: 15
#| fig-height: 5

sphericalspiral_proj1 + sphericalspiral_proj2 + sphericalspiral_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-helicalspiral, echo=TRUE}
helicalspiral <- gen_helicalspiral(n = 1000, p = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(helicalspiral)
```

```{r helicalspiral-proj1}
scaled_data <- scale_data_manual(helicalspiral)

helicalspiral_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r helicalspiral-proj2}

helicalspiral_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r helicalspiral-proj3}

helicalspiral_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-helicalspiral-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `helicalspiral` data."}
#| fig-width: 15
#| fig-height: 5

helicalspiral_proj1 + helicalspiral_proj2 + helicalspiral_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-conicspiral, echo=TRUE}
conicspiral <- gen_conicspiral(n = 1000, p = 4, spins = 1)
```

```{r, eval=FALSE}
langevitour::langevitour(conicspiral)
```

```{r conicspiral-proj1}
scaled_data <- scale_data_manual(conicspiral)

conicspiral_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r conicspiral-proj2}

conicspiral_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r conicspiral-proj3}

conicspiral_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-conicspiral-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `conicspiral` data."}
#| fig-width: 15
#| fig-height: 5

conicspiral_proj1 + conicspiral_proj2 + conicspiral_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-nonlinear, echo=TRUE}
nonlinear <- gen_nonlinear(n = 1000, p = 4, hc = 1, non_fac = 0.5)
```

```{r, eval=FALSE}
langevitour::langevitour(nonlinear)
```

```{r nonlinear-proj1}
scaled_data <- scale_data_manual(nonlinear)

nonlinear_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r nonlinear-proj2}

nonlinear_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r nonlinear-proj3}

nonlinear_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-nonlinear-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `nonlinear` data."}
#| fig-width: 15
#| fig-height: 5

nonlinear_proj1 + nonlinear_proj2 + nonlinear_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```
